Figures and results for main manuscript

### 2020-12-17 analysis/reports/manuscript_main.Rmd
tweaks ad updates

fig_3 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y") +
    xlab("Breadth index") +
    ylab("Number of communities") +
    ggtitle("Skewness"),

  ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y") +
    xlab("Breadth index") +
    ylab("Number of communities") +
    ggtitle("Evenness")
))

@@

```{r}
pdf("figure_1.pdf")
plot(fig_1)
dev.off()

pdf("figure_2.pdf")
 plot(fig_2)
 dev.off()

pdf("figure_3.pdf")
plot(fig_3)
dev.off()

pdf("figure_4.pdf")
 plot(fig_4)
dev.off()
```

>>>>

fig_3 <- gridExtra::grid.arrange(grobs = list(
  ggplot(filter(all_di, s0 > 2, skew_unique > 20), aes(x= skew_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y") +
    xlab("Breadth index (ranges 0-1, with 1 being very broad)") +
    ylab("Number of communities") +
    ggtitle("Skewness"),

  ggplot(filter(all_di, simpson_unique > 20), aes(x = simpson_95_ratio_1t)) +
    geom_histogram() +
    theme_bw() +
    facet_wrap(vars(Dataset), scales = "free_y") +
    xlab("Breadth index (ranges 0-1, with 1 being very broad)") +
    ylab("Number of communities") +
    ggtitle("Evenness")
))

@@

```{r}
pdf("figure_1.pdf", title = "Figure 1")
plot(fig_1)
dev.off()

pdf("figure_2.pdf", title = "Figure 2")
 plot(fig_2)
 dev.off()

pdf("figure_3.pdf", title = "Figure 3")
plot(fig_3)
dev.off()

pdf("figure_4.pdf", title = "Figure 4")
 plot(fig_4)
dev.off()
```
